### 2019-06-18 manuscript/Manuscript.Rnw
Updated Manuscript

\subsection{Statistical Shape Analysis}
Much of the early work in shape analysis was based on defining shapes by a series of landmarks (\cite{Bookstein1986,MardiaAndDryden1989,Kendall1984,LeAndKendall1993}) where each point represents a meaningful location on a shape and there is a natural correspondence between points across shapes in a sample.  This allows for a natural correspondence of points across shapes and greatly simplifies analysis in many cases, such as computing a mean shape or variability of a collection of shapes.  The use of landmark data also allows for a natural methods for the alignment of shapes to one another using a method called Procrustes analysis \cite{Green1952,Goodall1991}, which aligns shapes subject to translations, rotations, and scaling.  Additionally, shapes can be defined by unlabeled points where there is some true labeling, but it is unobserved.  This setting is more complicated than labeled landmarks since the correspondence between points across shapes is unknown.  In many situations, however, there are no reasonable choices for landmarks on the shape.

Later, \citet{Bookstein1997} defined the concept of slidibng landmarks.   WHAT ARE THESE......explain.

>>>>

\subsection{Statistical Shape Analysis}
\subsection{Landmarks}
Much of the early work in shape analysis was based on defining shapes by a series of landmarks (\cite{Bookstein1986,MardiaAndDryden1989,Kendall1984,LeAndKendall1993}) where each point represents a meaningful location on a shape and there is a natural correspondence between points across shapes in a sample.  This allows for a natural correspondence of points across shapes and greatly simplifies analysis in many cases, such as computing a mean shape or variability of a collection of shapes.  The use of landmark data also allows for a natural methods for the alignment of shapes to one another using a method called Procrustes analysis \cite{Green1952,Goodall1991}, which aligns shapes subject to translations, rotations, and scaling.  Additionally, shapes can be defined by unlabeled points where there is some true labeling, but it is unobserved.  This setting is more complicated than labeled landmarks since the correspondence between points across shapes is unknown.  In many situations, however, there are no reasonable choices for landmarks on the shape.  Later,the concept of sliding landmarks \citet{Green1996, Bookstein1997} was proposed.  Sliding landmarks are the same as landmarks except that they are allowed to ``slide" along the contour of the curve when being aligned with a reference set of landmarks.

\subsection{Continuous Curves}
Rather than
